The Poisson approximate likelihood compared to the particle filter

### 2024-08-21 ms.Rnw
a few edits
table moving
ms on gl

RUN_LEVEL = 1
NP_MIF       = switch(RUN_LEVEL, 10,   5000,  50000)
NMIF         = switch(RUN_LEVEL, 5,    20,    100)
ncores       = switch(RUN_LEVEL, 4,    10,    36)
top_n_fits   = switch(RUN_LEVEL, 1,    2,     12)
sim_rep      = switch(RUN_LEVEL, 5,    20,    100) #sim_ovov

@@

>>>>

RUN_LEVEL = 3
NP_MIF       = switch(RUN_LEVEL, 10,   5000,  50000)
NMIF         = switch(RUN_LEVEL, 5,    20,    100)
ncores       = switch(RUN_LEVEL, 4,    10,    36)
top_n_fits   = switch(RUN_LEVEL, 1,    2,     12)
sim_rep      = switch(RUN_LEVEL, 5,    20,    100) #sim_ovov

@@

\yize{ON AVERAGE PAL IS 25.3 LOG UNITS LOWER THAN PFILTER AND SHOULD WE MENTION THAT WE USED THE SIMULATED DATA WITHOUT ZEROS? \\ 
THE TABLE SEEMS TO BE TALL AND THIN. SHOULD WE PUT IT IN A APPENDIX?}
